\textbf{Three equanimous aspects\\of scale-free networks}\\

### 2015-02-12 essay.tex
atualizando com links de trabalhos para ler em breve

\subsection{Related work}\label{sec:rel}
The complex network literature stresses concentration and revolves around the hub. 
More accurately, it glamorizes the most connected nodes as ``both the strength and the weakness of scale-free networks''~\cite{wikipedia}, and put them as the most important vertexes. This is naive for a number of reasons:
\begin{itemize}
    \item Hubs are but a few vertexes, which are replaced constantly.
    \item Hubs present the most trivial behavior: they interact as much as possible, in every situation, with everyone. That is one of the core reasons why they are hubs.
    \item Hubs tend to present corrupt behavior, as they wage huge amounts of time and energy on the network and frequently depend on such activities for basic provision.
    \item World input to the network is done by periphery and intermediary vertexes, as they do not wage all their energy on the network.
    \item Authorities are often intermediaries or less active hubs, specially in cases where they deliver quality, not quantity.
    \item Network structure is given by intermediary vertexes, as they are the only with non trivial behavior: peripheral vertexes interact only a few times; hubs interact everywhere possible.
\end{itemize}

@@

\section{Canonical background}\label{sec:can}
Networks with a power law distribution of connectivity (degree) are called scale-free. In other words, be $p(k)$ the probability that an arbitrary vertex has degree $k$, than, for a scale-free network, one can assume:
\begin{equation}
p(k) \sim k^{-\gamma}
\end{equation}
\noindent where $\gamma > 1$ is constant and typically $\gamma \in [2,3]$. This same distribution is called, under certain conditions, the Pareto distribution or the Zipf law.

\subsection{Zipf law}
\subsection{Pareto distribution}
\subsection{Scale-free networks}

>>>>

\subsection{Related work}\label{sec:rel}
The complex network literature stresses concentration and revolves around the hub. 
More accurately, it glamorizes the most connected nodes as ``both the strength and the weakness of scale-free networks''~\cite{wikipedia}, and put them as the most important vertexes. This is naive for a number of reasons. Put in social networks terms, often used for such discussions:
\begin{itemize}
    \item Hubs are but a few vertexes, which are replaced constantly.
    \item Hubs present the most trivial behavior: they interact as much as possible, in every situation, with every other agent. That is a prerequisite for they to be hubs.
    \item Hubs tend to present corrupt behavior, as they wage huge amounts of time and energy on the network and frequently depend on such activities for basic provision.
    \item World input to the network is done by periphery and intermediary agents, as they do not wage all their energy on the network.
    \item Authorities are often intermediaries or less active hubs, specially in cases where they deliver quality, not quantity.
    \item Network structure is given by intermediary vertexes, as they are the only with non trivial behavior: peripheral vertexes interact only a few times; hubs interact everywhere possible.
\end{itemize}

@@

\section{Canonical background}\label{sec:can}
Networks with a power law distribution of connectivity (degree) are called scale-free. In other words, be $p(k)$ the probability that an arbitrary vertex has degree $k$, than, for a scale-free network, one can assume:
\begin{equation}
p(k) \sim k^{-\gamma}
\end{equation}
\noindent where $\gamma > 1$ is constant and typically $\gamma \in [2,3]$. This same distribution is called, under certain conditions, the Pareto distribution or the Zipf law. In fact, they all report that nature distribute resources in power laws.

LER AO MENOS: \url{http://www.nature.com/nature/journal/v435/n7039/full/nature03459.html} e \url{https://www.pik-potsdam.de/members/kurths/publikationen/2010/pnas-18803.full.pdf}.

\subsection{Zipf law}
\subsection{Pareto distribution}
\subsection{Scale-free networks}
\subsection{Human perception}
Webner-Fechner law.
